Web Scraping: attempt 2

### 2017-04-08 Web_Scraping_attempt3.Rmd
Add files via upload

*html_session within function *

4/8/17  1:44pm    SYSTEM.TIME:  336.107 seconds elapsed

@@

grab_temps <- function(link){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0("KDSM/",link))
  html <- read_html(ss)

@@

    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
                      mean_max_min = as.character(rep(temp, times = 2)),
                      actual_ave = as.character(rep(c("Actual", "Historical Average"), each = 3)),
                      value = as.numeric(c(actual_vals, average_vals))))
}

## WORKING ###
df2 <- data.frame(Links = links[1:365])
system.time(df2 %>% nest() %>% mutate(daily_temps = Links %>% purrr::map(grab_temps))) #%>% select(-Links) %>% unnest()
##############

@@

*Pasting togeter url and then using read_html*

4/8/17  1:52pm   SYSTEM.TIME:   343.802 elapsed

```{r}

grab_temps2 <- function(date){
    url <- paste0("https://www.wunderground.com/history/airport/", "KDSM/", date, "/DailyHistory.html") # Pasting together parts of url
    html <- read_html(url)

    return(data.frame(day = as.Date(substring(text = link, first = 1, last = 10)),
                      mean_max_min = as.character(rep(temp, times = 2)),
                      actual_ave = as.character(rep(c("Actual", "Historical Average"), each = 3)),
                      value = as.numeric(c(actual_vals, average_vals))))
}

link_dates <- gsub(pattern = "-", replacement = "/", x = seq(from = as.Date("1945-01-01"), to = Sys.Date(), by = "days"))
airport <- "KDSM/"

## WORKING ###
df3 <- data.frame(Dates = link_dates[1:365])
system.time(df3 %>% nest() %>% mutate(daily_temps = Dates %>% purrr::map(grab_temps2))) #%>% select(-Links) %>% unnest()
##############

>>>>

*html_session within function with record inside the function (and not a separate function)*

@@

grab_temps <- function(link){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0("KDSM/", link))
  html <- read_html(ss)

@@

    record <- html %>% 
      html_nodes("#historyTable tr:nth-child(4) td:nth-child(4) , #historyTable tr:nth-child(3) td:nth-child(4)") %>%
      html_text()
    record_vals <- c("NA", parse_number(record))
    record_yrs <- record %>% gsub("^[^\\(]+", "", .) %>% parse_number()

    return(data.frame(day = as.Date(c(rep(substring(text = link, first = 1, last = 10), times = 6), "NA",
                              paste0(record_yrs, substring(text = link, first = 5, last = 10)))),
                      mean_max_min = as.character(rep(temp, times = 3)),
                      actual_ave_rec = as.character(rep(c("Actual", "Historical Average", "Record"), each = 3)),
                      value = as.numeric(c(actual_vals, average_vals, record_vals))))
}

df2 <- data.frame(Links = links[1:3])  ## for first 3 'days'
df2 %>% nest() %>% mutate(daily_temps = Links %>% purrr::map(grab_temps)) %>% select(-Links) #%>% unnest()

@@
